Social Feedback For Robotic Collaboration

### 2016-05-19 paper.tex
put stuff from appendix into text

$$p(o|s) = \eta \frac{p(o|\iota) \beta(\iota)}{\sum_{\iota^\prime} p(o|\iota^\prime)\beta(\iota^\prime)} $$

@@

Using $\beta$ as a prior for our observation function incentivizes the robot to take actions that modify $\beta$ in such a way that increase the probability of useful observations, while in turn decreasing the probability of getting observations that tell the robot things it already knows. This result falls out of our assumption that the human is more likely to provide observations that communicate its intentions to the robot well.\footnote{It is perhaps more accurate to say that the human does not pick proportional to the probability, but picks the action with the greatest value  of $p(\iota|o)$. However, this deterministic observation function would lead to irregularities when faced with real human users who do not pick perfectly. Using a softmax function with a tuned temperature parameter would allow us to balance the strong guarantees of of a deterministic max with the flexibility of ``proportional to probability''.}  For a worked example in a toy domain, see the appendix.

@@

This requires us to specify $p(a_{t} | \iota_{t+1})$. Recall that actions are operating as observations from the perspective of the human, making this expression a \emph{reverse observation function}. We must provide a reverse observation function for each action. These will often be very similar to the base-level observations described in Section \ref{sssec:of}, though adapted slightly to suit being performed by a Baxter robot. See the appendix for details.

@@

where $A_{t}$ is a matrix representing the reverse observation function $p(a_{t} | \iota_{t+1})$ and $T$ is a matrix representing the transition function $p(\iota_{t+1}|\iota_{t})$.  If the set of items $\mathcal{\iota} = \{ \iota_1, \iota_2, \ldots, \iota_n\}$, A is a diagonal such that

\begin{equation*}
	a_{ij} = \begin{cases}
		0 & \text{if } i \ne j \\
		p(a_t | \iota_{t+1} = \iota_i & \text{otherwise}
	\end{cases}
\end{equation*}

@@

@@

\newpage
\section{Appendix}

\subsection{Posterior Observation Function: Toy Example}
In order to demonstrate and motivate the posterior observation function, we will define a toy domain. In this toy domain, the states are the following: $\{AA, AB, BA, BB\}$ as well as $\beta$, which is a distribution over these states. The observations are $\{A\_, \_A, B\_, \_B\}$, which mean ``the first character is an A'', ``the second character is an A'', ``the first character is B'', ``and the second character is a B'' respectively. These observations are provided by the human. The agent can take actions $CX$ which is informing the human that the agent believes the Xth character is a C, as well as ``picking'' the object or waiting. For the basel level observation, the human always gives truthful observations, and has equal probability of generating an observation pertaining to a particular character. We will see how this affects the POMDP observation function, which incorporates $\beta$.

\begin{center}
\begin{tabular}{|c| c| c| c | c|}
	\hline
	$t$ & $b$ & $\beta$ & $a$ & $o$ \\
	\hline
	$0$ & [0.25, 0.25, 0.25, 0.25] & [0.25, 0.25, 0.25, 0.25] & & \\
	\hline
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{|c| c| c| c | c|}
	\hline
	$t$ & $b$ & $\beta$ & $a$ & $o$ \\
	\hline
	$0$ & [0.25, 0.25, 0.25, 0.25] & [0.25, 0.25, 0.25, 0.25] & & \\
	\hline
	$1$ & [0.50, 0.50, 0, 0] & [0.25, 0.25, 0.25, 0.25] & & $A\_$ \\
	\hline
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{|c| c| c| c | c|}
	\hline
	$t$ & $b$ & $\beta$ & $a$ & $o$ \\
	\hline
	$0$ & [0.25, 0.25, 0.25, 0.25] & [0.25, 0.25, 0.25, 0.25] & & \\
	\hline
	$1$ & [0.50, 0.50, 0, 0] & [0.25, 0.25, 0.25, 0.25] & & $A\_$ \\
	\hline
	$2$ & [0.50, 0.50, 0, 0] & [0.25, 0.25, 0.25, 0.25] & wait  &  \\
	\hline
\end{tabular}
\end{center}

\begin{align*}
	p(A\_ | AA, \beta) &= \frac{ p(A\_)\beta(AA) }{ p(A\_)\beta(AA) + p(A\_)\beta(AB) + p(A\_)\beta(BA) + p(A\_)\beta(BB)} \\
	&= \frac{0.5 * 0.25}{0.5 * 0.25 + 0.5 * 0.25 + 0 + 0} \\
	&= 0.5
\end{align*}

\begin{align*}
	p(\_A | AA, \beta) &= \frac{ p(\_A)\beta(AA) }{ p(\_A)\beta(AA) + p(\_A)\beta(AB) + p(\_A)\beta(BA) + p(\_A)\beta(BB)} \\
	&= \frac{0.5 * 0.25}{0.5 * 0.25 + 0 + 0.5 * 0.25 + 0} \\
	&= 0.5
\end{align*}

Notice that this situation is not ideal. The agent has equal probabilities of receiving either observation, even though the agent already knows that the first character is an A. Now, consider what would happen if the robot chose the action $A0$. We would get the following belief states:

\begin{center}
\begin{tabular}{|c| c| c| c | c|}
	\hline
	$t$ & $b$ & $\beta$ & $a$ & $o$ \\
	\hline
	$0$ & [0.25, 0.25, 0.25, 0.25] & [0.25, 0.25, 0.25, 0.25] & & \\
	\hline
	$1$ & [0.50, 0.50, 0, 0] & [0.25, 0.25, 0.25, 0.25] & & $A\_$ \\
	\hline
	$2$ & [0.50, 0.50, 0, 0] & [0.5, 0.5, 0, 0] & $A0$  &  \\
	\hline
\end{tabular}
\end{center}

\begin{align*}
	p(A\_|AA, \beta) &\propto \frac{ p(A\_)\beta(AA) }{ p(A\_)\beta(AA) + p(A\_)\beta(AB) + p(A\_)\beta(BA) + p(A\_)\beta(BB)} \\
	&\propto \frac{0.5 * 0.5}{0.5 * 0.5 + 0.5 * 0.5 + 0 + 0} \\
	&\propto 0.5 \\
	&= \frac{1}{3}
\end{align*}

\begin{align*}
	p(\_A|AA, \beta) &\propto \frac{ p(\_A)\beta(AA) }{ p(\_A)\beta(AA) + p(\_A)\beta(AB) + p(\_A)\beta(BA) + p(\_A)\beta(BB)} \\
	&\propto \frac{0.5 * 0.5}{0.5 * 0.5 + 0 + 0 + 0} \\
	&\propto 1 \\
	&= \frac{2}{3}
\end{align*}

Now, we are more likely to get the observation $\_A$, which is more useful to us than the observation $A\_$, since it gives us the information we need to pick the correct object, $AA$. This provides an incentive for the robot to choose an action that conveys something about its current state of belief over doing nothing.

\subsection{Reverse Observation Functions}

>>>>

$$p(i|o) = \eta \frac{p(o|\iota) \beta(\iota)}{\sum_{\iota^\prime} p(o|\iota^\prime)\beta(\iota^\prime)} $$

@@

Using $\beta$ as a prior for our observation function incentivizes the robot to take actions that modify $\beta$ in such a way that increase the probability of useful observations, while in turn decreasing the probability of getting observations that tell the robot things it already knows. This result falls out of our assumption that the human is more likely to provide observations that communicate its intentions to the robot well. Consider the following example:

First, we will define a toy domain. In this toy domain, the states are the following: $\{AA, AB, BA, BB\}$ as well as $\beta$, which is a distribution over these states. The observations are $\{A\_, \_A, B\_, \_B\}$, which mean ``the first character is an A'', ``the second character is an A'', ``the first character is B'', ``and the second character is a B'' respectively. These observations are provided by the human. The agent can take actions $CX$ which is informing the human that the agent believes the Xth character is a C, as well as ``picking'' the object or waiting. For the basel level observation, the human always gives truthful observations, and has equal probability of generating an observation pertaining to a particular character. We will see how this affects the POMDP observation function, which incorporates $\beta$.

\begin{center}
	\footnotesize
\begin{tabular}{|c| c| c| c | c|}
	\hline
	$t$ & $b$ & $\beta$ & $a$ & $o$ \\
	\hline
	$0$ & [0.25, 0.25, 0.25, 0.25] & [0.25, 0.25, 0.25, 0.25] & & \\
	\hline
\end{tabular}
\end{center}

\begin{center}
	\footnotesize
\begin{tabular}{|c| c| c| c | c|}
	\hline
	$t$ & $b$ & $\beta$ & $a$ & $o$ \\
	\hline
	$0$ & [0.25, 0.25, 0.25, 0.25] & [0.25, 0.25, 0.25, 0.25] & & \\
	\hline
	$1$ & [0.50, 0.50, 0, 0] & [0.25, 0.25, 0.25, 0.25] & & $A\_$ \\
	\hline
\end{tabular}
\end{center}

\begin{center}
	\footnotesize
\begin{tabular}{|c| c| c| c | c|}
	\hline
	$t$ & $b$ & $\beta$ & $a$ & $o$ \\
	\hline
	$0$ & [0.25, 0.25, 0.25, 0.25] & [0.25, 0.25, 0.25, 0.25] & & \\
	\hline
	$1$ & [0.50, 0.50, 0, 0] & [0.25, 0.25, 0.25, 0.25] & & $A\_$ \\
	\hline
	$2$ & [0.50, 0.50, 0, 0] & [0.25, 0.25, 0.25, 0.25] & wait  &  \\
	\hline
\end{tabular}
\end{center}

\begin{align*}
	p(A\_ | AA, \beta) &= \frac{ p(A\_)\beta(AA) }{ \sum_{h \in \{AA, AB, BA, BB\}} p(A\_ | h) } \\
	&= \frac{0.5 * 0.25}{0.5 * 0.25 + 0.5 * 0.25 + 0 + 0} \\
	&= 0.5
\end{align*}

\begin{align*}
	p(\_A | AA, \beta) & \\
	&= \frac{ p(\_A)\beta(AA) }{ \sum_{h \in \{AA, AB, BA, BB\}} p(\_A | h) } \\
	&= \frac{0.5 * 0.25}{0.5 * 0.25 + 0 + 0.5 * 0.25 + 0} \\
	&= 0.5
\end{align*}

Notice that this situation is not ideal. According to the human, producing each of these observations equally optimal, so we are equally likely to see either observation in this situation, even though the agent already knows that the first character is an A. Now, consider what would happen if the robot chose the action $A0$. We would get the following belief states:

\begin{center}
	\footnotesize
\begin{tabular}{|c| c| c| c | c|}
	\hline
	$t$ & $b$ & $\beta$ & $a$ & $o$ \\
	\hline
	$0$ & [0.25, 0.25, 0.25, 0.25] & [0.25, 0.25, 0.25, 0.25] & & \\
	\hline
	$1$ & [0.50, 0.50, 0, 0] & [0.25, 0.25, 0.25, 0.25] & & $A\_$ \\
	\hline
	$2$ & [0.50, 0.50, 0, 0] & [0.5, 0.5, 0, 0] & $A0$  &  \\
	\hline
\end{tabular}
\end{center}

\begin{align*}
	p(A\_|AA, \beta) & \\
	&= \frac{ p(A\_)\beta(AA) }{ \sum_{h \in \{AA, AB, BA, BB\}} p(A\_ | h) } \\
	&= \frac{0.5 * 0.5}{0.5 * 0.5 + 0.5 * 0.5 + 0 + 0} \\
	&= 0.5 \\
\end{align*}

\begin{align*}
	p(\_A|AA, \beta) &\propto \frac{ p(\_A)\beta(AA) }{ \sum_{h \in \{AA, AB, BA, BB\}} p(\_A | h) } \\
	&= \frac{0.5 * 0.5}{0.5 * 0.5 + 0 + 0 + 0} \\
	&= 1 \\
\end{align*}

Now, observation $\_A$ is the most optimal, so there is high probability the human will generate this observation for the robot. This observation will give the robot the information it needs to pick the correct object, $AA$. This provides an incentive for the robot to choose an action that conveys something about its current state of belief over doing nothing.

@@

This requires us to specify $p(a_{t} | \iota_{t+1})$. Recall that actions are operating as observations from the perspective of the human, making this expression a \emph{reverse observation function}. We must provide a reverse observation function for each action. These will often be very similar to the base-level observations described in Section \ref{sssec:of}, though adapted slightly to suit being performed by a Baxter robot. See section ~\ref{reverse} for details.

@@

where $A_{t}$ is a matrix representing the reverse observation function $p(a_{t} | \iota_{t+1})$ and $T$ is a matrix representing the transition function $p(\iota_{t+1}|\iota_{t})$.  If the set of items $\mathcal{\iota} = \{ \iota_1, \iota_2, \ldots, \iota_n\}$, A is a diagonal matrix such that

\begin{equation*}
	a_{ij} = \begin{cases}
		0 & \text{if } i \ne j \\
		p(a_t | \iota_{t+1}) = \iota_i & \text{otherwise}
	\end{cases}
\end{equation*}

@@

\paragraph{Reverse Observation Functions} \label{reverse}

@@
